\documentclass[10pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.8in]{geometry}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}

\definecolor{accent}{HTML}{4C3AAF}
\newcommand{\code}[1]{\texttt{#1}}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}

\titleformat{\section}{\normalsize\bfseries\color{accent}}{}{0em}{}
\titlespacing*{\section}{0pt}{0.8em}{0.3em}
\setlength{\parskip}{0.3em}
\setlength{\parindent}{0pt}
\pagestyle{empty}

\begin{document}

\begin{center}
    {\Large\bfseries Tool Disclosure Document}\\[2pt]
    {\small CSAI 422 Capstone \textemdash{} E-Commerce Customer Support Agent (``TechMart'') \quad|\quad Project Option A}
\end{center}
\vspace{2pt}\hrule

Every external framework, library, dataset, and AI assistant used in this project, with a brief
justification and its role in the architecture.

\section{Frameworks \& Libraries}
\small
\begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}p{3.4cm}>{\raggedright\arraybackslash}p{1.5cm}Y@{}}
\toprule
\textbf{Tool} & \textbf{Version} & \textbf{Purpose / Role in architecture} \\
\midrule
LangGraph & 1.2.2 & Multi-agent orchestration: graph topology, shared state, conditional routing (required framework). \\
langgraph-checkpoint-sqlite & 3.1.0 & \code{SqliteSaver} checkpointer \textemdash{} short-term per-thread conversation memory. \\
LangChain & 1.3.2 & LLM abstraction, document types, embedding/retriever interfaces. \\
langchain-openai & 1.2.2 & OpenAI chat-model and embedding wrappers. \\
langchain-community & 0.4.2 & Community integrations (BM25 retriever and utilities for hybrid search). \\
langchain-chroma & 1.1.0 & Chroma vector-store integration for LangChain. \\
ChromaDB & 1.5.9 & Persistent vector store for RAG document embeddings + metadata filtering. \\
rank-bm25 & 0.2.2 & BM25 lexical search \textemdash{} the sparse half of hybrid retrieval. \\
sentence-transformers & 4.1.0 & Cross-encoder reranking (\code{ms-marco-MiniLM-L-6-v2}) in the final RAG pipeline. \\
Faker & 40.19.1 & Synthetic order-data generation (220 orders, 50 customers, 5 statuses). \\
Streamlit & 1.58.0 & Observability dashboard: live chat, routing decisions, memory panel, RAGAS results (\emph{implemented}). \\
python-dotenv & 1.2.2 & Environment-variable / API-key management. \\
Pydantic & 2.13.4 & Data validation and typed state schema. \\
\bottomrule
\end{tabularx}
\normalsize

\section{LLM \& Embedding Models}
\small
\begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}p{4.0cm}>{\raggedright\arraybackslash}p{2.4cm}Y@{}}
\toprule
\textbf{Model} & \textbf{Provider} & \textbf{Purpose} \\
\midrule
\code{gpt-4o-mini}             & OpenAI       & Supervisor intent classification, agent responses, RAG generation, and RAGAS-style LLM-as-judge scoring. \\
\code{text-embedding-3-small}  & OpenAI       & Dense document and query embeddings for Chroma. \\
\code{ms-marco-MiniLM-L-6-v2}  & Hugging Face & Cross-encoder reranking of retrieval candidates. \\
\bottomrule
\end{tabularx}
\normalsize

\section{Datasets}
\small
\begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}p{3.4cm}>{\raggedright\arraybackslash}p{3.0cm}Y@{}}
\toprule
\textbf{Dataset} & \textbf{Source} & \textbf{Purpose} \\
\midrule
Synthetic orders (\code{orders.json}) & Generated with Faker (seeded) & Mock order-API data \textemdash{} 220 orders across 5 statuses, 50 customers. \\
Policy documents & Hand-authored & Shipping and returns/refund policies for the fictional TechMart store. \\
Product catalog & Hand-authored & 8 electronics products with specs, prices, and warranty terms. \\
FAQ document & Hand-authored & 20 Q\&A pairs covering common customer questions. \\
Gold eval set (\code{gold\_qa.json}) & Hand-authored & 20 Q\&A pairs with ground-truth answers for RAGAS evaluation. \\
\bottomrule
\end{tabularx}
\normalsize

\textbf{Note on the knowledge base.} All policy, catalog, and FAQ documents were \emph{hand-authored}
(not LLM-generated) to retain full control over ground truth, making retrieval quality measurable.
Order records are synthetic (Faker), per the brief's requirement to avoid real order data.

\section{AI Assistants}
\small
\begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}p{3.4cm}Y@{}}
\toprule
\textbf{Assistant} & \textbf{Usage} \\
\midrule
Claude (Anthropic) & Code generation, architecture guidance, implementation assistance, and debugging. \\
\bottomrule
\end{tabularx}
\normalsize

\section{Design Note}
The \code{ragas} library was intentionally \emph{not} used: releases 0.1.x--0.4.x conflict with
\code{langchain-core} $\geq$ 1.4 (required by \code{langgraph} 1.2). The four RAGAS metrics were
reimplemented as an LLM-as-judge, giving equivalent measurements with full control. \textbf{All
architectural and design decisions were reviewed and are understood by every team member.}

\end{document}
